A performance assessment of evolutionary algorithms in volunteer computing environments: the importance of entropy

### 2016-11-15 EvoPar2017/paper.tex
Reviewed the state of the art, fixed some typos. References #132

Volunteer computing involves users deciding to run a program that acts
as a client or as a peer in an experiment
and, as such, has been deployed in many different ways from the
beginning of the Internet, starting with the SETI@home framework for
processing extraterrestrial signals \cite{david-seti:home} or
high-throughput queuing system that such as HTCondor \cite{HTCondor}.
However
the dual facts of the introduction of JavaScript as a universal language for the
browser and the browser itself as an ubiquitous web and Internet client has
made this combination the most popular for volunteer computing
frameworks such as the one we are using here, and whose first version
was described in [citation hidden]. Systems based on the
JavaScript/browser combination
emphasize the ephemerality, ease of use and universality, while
systems such as HTCondor or BOINC might be more adequate for work that
require higher availability of volunteer resources, achieving this
with downloadable clients, in some cases like HTCondor needing
administration access to the resources.
%\cite{DBLP:conf/gecco/GuervosG15anonymous}.

@@

Using a peer to peer approach, the SPACE framework \cite{leclerc2016seamless} distributes fitness 
evaluations across a heterogeneous pool of cloud compute nodes and volunteer
peer computers running a browser. In SPACE peers stablis a bi-directional 
communication with the server using the Socket.io JavaScript library.  
As an experiment they provide an ASM.js compiled version of the RoboGen 
software platform, showing that JavaScript can be used in a broad 
spectrum of applications.

Recent works have been using crowdsourcing in order to train robots 
for human interaction, a representative work of this trend is that of  
Anetsberger \& Bongard \cite{anetsbergerrobots} in which they propose 
training simulated robots  the grounding of language symbols. They do this by using human 
observers that issue arbitrary commands to these robots via the web, 
providing positive or negative reinforcement in response to the
robot\'s resulting actions. For interaction, they use the Twitch 
video streaming platform where users can issue commands through the
platform's integrated chat service. Subjects were incentivized to 
interact with the system by GUI features that provided participants
with a sense of involvement with the simulation. This kind of systems
could add additional dynamics, because users can collaborate or 
even compete with each other when issuing their commands.

@@

The proof of concepts described above do not go further than trying to
find out  how many users join the effort and how many the system is
able to support. In fact, systems described in
\cite{gecco07:workshop:dcor} had serious scaling issues; some of them
also tried to find out how much time was needed to find the solution
or, alternatively, how many users would be needed to be competitive
with single-user single-computer implementations of the same
algorithm. However, the latest systems try to enphasize the seamless
integration of peer and volunteer computing systems \cite{leclerc2016seamless}.

This latest system offloads evaluation to browsers so the actual
algorithm runs in some other place; in general, most researchers do
not try to assess the performance of the algorithm 
itself in the precise conditions they find in a volunteer computing
system, although papers such as the one by Laredo et
al. \cite{churn08:ijhpsa}, using models, try to find out the resulting
performance when the users are changing continuously according to a
Weibull distribution. In the case of Klein and Spector \cite{unwitting-ec}, the algorithm
is actually run on the server, using the browser mainly for fitness
evaluation so no actual contribution to the evaluation of the
evolutionary algorithm itself is made.

>>>>

Volunteer computing involves users deciding to run a program that acts
as a client or as a peer in an experiment
and, as such, has been deployed in many different ways from the
beginning of the Internet, starting with the SETI@home framework for
processing extraterrestrial signals \cite{david-seti:home}, or a 
high-throughput queuing system such as HTCondor \cite{HTCondor}.
However,
the dual facts of the introduction of JavaScript as a universal language for the
browser and the browser itself as both an ubiquitous web and Internet client has
made this combination the most popular for volunteer computing
frameworks such as the one we are using here, and whose first version
was described in \cite{DBLP:conf/gecco/GuervosG15anonymous}. Systems based on the
JavaScript/browser combination
emphasize the ephemerality, ease of use, and universality, while
systems such as HTCondor or BOINC might be more adequate for work that % citation for BOINC (?)
require higher availability of volunteer resources, achieving this
with downloadable clients which in some cases, like HTCondor, need
administration access to the resources.

@@

Using a peer to peer approach, the SPACE framework \cite{leclerc2016seamless} distributes fitness 
evaluations across a heterogeneous pool of cloud compute nodes and volunteer
peer computers running a browser. In SPACE peers establish a bi-directional 
communication with the server using the \texttt{Socket.io} JavaScript library.  
As an experiment they provide an \texttt{ASM.js} compiled version of the RoboGen 
software platform, showing that JavaScript can be used in a broad 
spectrum of applications.

Recent works have been using crowdsourcing in order to train robots 
for human interaction, a representative work of this trend is that of  
Anetsberger \& Bongard \cite{anetsbergerrobots} in which they propose 
training simulated robots for the grounding of language symbols. They do this by using human 
observers that issue arbitrary commands to these robots via the web, 
providing positive or negative reinforcement in response to the
robot\'s resulting actions. For interaction, they use the Twitch 
video streaming platform where users can issue commands through the
platform's integrated chat service. Subjects were incentivized to 
interact with the system by GUI features that provided participants
with a sense of involvement with the simulation. This kind of systems
could add additional dynamics, because users can collaborate or 
even compete with each other when issuing their commands.

@@

The proofs of concept described above do not go further than trying to
find out  how many users join the effort and how many the system is
able to support. In fact, systems described in
\cite{gecco07:workshop:dcor} had serious scaling issues; some of them
also tried to find out how much time was needed to find the solution
or, alternatively, how many users would be needed to be competitive
with single-user single-computer implementations of the same
algorithm. However, the latest systems try to emphasize the seamless
integration of peer and volunteer computing systems \cite{leclerc2016seamless}.

This latest system offloads evaluation to browsers so the actual
algorithm runs in some other place; in general, most researchers do
not try to assess the performance of the algorithm 
itself in the precise conditions they find in a volunteer computing
system, although papers such as the one by Laredo et
al. \cite{churn08:ijhpsa}, using models, try to find out the resulting
performance when the users are changing continuously according to a
Weibull distribution. In the case of Klein and Spector \cite{unwitting-ec}, the algorithm
is actually run on the server, using the browser mainly for fitness
evaluation, and thus no actual contribution to the evaluation of the
evolutionary algorithm itself is made.
